---
title: "Data Science Homework 1"
author: "Shiqi Wu"
data: 2023-09-23
output: github_document
---

# Problem 1

```{r setup}
library(moderndive)
data("early_january_weather")
```

```{r dataset}
num_rows <- nrow(early_january_weather)
num_cols <- ncol(early_january_weather)
mean_temp <- mean(early_january_weather$temp)
```

The dataset contains weather-related information recorded at various time points.
The variables in the `early_january_weather` dataset include `origin`, `year`,`month`,`day`,`hour`,`temp`,`dewp`,`humid`,`wind_dir`,`wind_speed`,`wind_gust`,`precip`,`pressure`,`visib`,`time_hour`. 
There are `15 columns` and `358 rows`. 
The `mean temperature` is `39.58 F`.

```{r plot}
library(ggplot2)
scatter_plot <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +
  geom_point() +
  labs(title = "Scatterplot of Temperature vs Time Hour",
       x = "Time Hour",
       y = "Temperature (°C)",
       color = "Humidity (%)") +
  theme_minimal()
ggsave("scatterplot_temperature_vs_time_hour.png", scatter_plot, width = 8, height = 6)
```

The plot reveals a clear `daily pattern` in temperature. The temperature tends to `rise during the daytime hours and fall during the nighttime hours`. The warmest temperatures are typically observed around midday. Humidity levels are generally `higher during the nighttime and early morning hours when temperatures are lower`. The `highest temperature on the 14th`. The `humidity from January 11th to 14th remained a high level (>80)`. There are also a few `outlier points` that deviate significantly from the main pattern.

# Problem 2

```{r}
library(tidyverse)

hw1_df = tibble(
  sample = rnorm(10),
  norm_sample_log = sample > 0, 
  vec_char = c("Rock","Jazz","Pop","Hip-hop","Classical","Country","Blues","Electronic","Reggae","R&B"),
  fac_char = factor(c("low","medium","high","low","medium","high","low","medium","high","low"))
)

mean(pull(hw1_df, sample))
mean(pull(hw1_df, norm_sample_log))
mean(pull(hw1_df, vec_char))
mean(pull(hw1_df, fac_char))
```

```{r numeric, results = 'hide', warning = FALSE}
as.numeric(pull(hw1_df,norm_sample_log))
as.numeric(pull(hw1_df,vec_char))
as.numeric(pull(hw1_df,fac_char))
```
At first, I can't calculate the mean of variable `vec_char` and `fac_char`.
`vec_char` is not numeric or logical, thus returning NA.
`fac_char` is not numeric or logical, thus returning NA.
After using `numeric function`, there are no more warnings. `norm_sample_log` and `fac_char` can be calculated. However, `vec_char` still returning NA.